Analysis of different methods for constructing continuous limits of agreement from smooth biomechanical data

### 2021-09-28 paper.Rmd
Adjust rmd file

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(boot)
# library(fda)
# library(funData)

@@

source("example_data.R")
# source("fdaDelta.R")
source("pick_subwise_curves.R")
source("draw_clusters.R")
source("floa_rcb.R")
source("floa_point.R")
source("floa_roislien.R")
source("plot_loa.R")
source("get_coverage.R")
source("get_coverage_fraction.R")
source("get_coverage_singlecurve.R")
source("get_coverage_singlecurve_fraction.R")
source("crossval_coverage.R")
source("crossval_coverage_fraction.R")
source("singlecurve_coverage.R")
source("singlecurve_coverage_fraction.R")
source("plot_cov_ver.R")
source("distance_2_floa.R")
source("estimate_uncertainty_loa.R")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_realistic", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_trend", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "non_gaussian", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "shift", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "imu_mc", dir.data)
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")
```

@@

covered.curves.percent <- apply(cover.cross.singlecurve, 2, calculate_percent)
covered.curves.percent <- data.frame(t(covered.curves.percent))
colnames(covered.curves.percent) <- c("RCB_2", "RCB_3", "Roislien_4", "Point_5")

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")

@@

c. Average distance to the outer point of the curve set
```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v2")
floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)

dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist,
                       distance_2_floa(data, floa)$lwr.dist,
                       distance_2_floa(data, floa.point)$upr.dist,
                       distance_2_floa(data, floa.point)$lwr.dist,
                       distance_2_floa(data, floa.roislien)$upr.dist,
                       distance_2_floa(data, floa.roislien)$lwr.dist
                       )

colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw")

boxplot(dist.all, ylab = "floa boundary - curve maximum")
```

d. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
estimate_uncertainty_loa(data, n.boot)
```

@@

c. Average distance to the outer point of the curve set
```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v2")
floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)

dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist,
                       distance_2_floa(data, floa)$lwr.dist,
                       distance_2_floa(data, floa.point)$upr.dist,
                       distance_2_floa(data, floa.point)$lwr.dist,
                       distance_2_floa(data, floa.roislien)$upr.dist,
                       distance_2_floa(data, floa.roislien)$lwr.dist
                       )

colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw")

boxplot(dist.all, ylab = "floa boundary - curve maximum")
```

d. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
# estimate_uncertainty_loa(data, n.boot)
```

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")
```

c. Average distance to the outer point of the curve set
```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v2")
floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)

dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist,
                       distance_2_floa(data, floa)$lwr.dist,
                       distance_2_floa(data, floa.point)$upr.dist,
                       distance_2_floa(data, floa.point)$lwr.dist,
                       distance_2_floa(data, floa.roislien)$upr.dist,
                       distance_2_floa(data, floa.roislien)$lwr.dist
                       )

colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw")

boxplot(dist.all, ylab = "floa boundary - curve maximum")
```

d. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
# estimate_uncertainty_loa(data, n.boot)
```

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points")

>>>>

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(boot)

@@

source("example_data.R")
source("pick_subwise_curves.R")
source("draw_clusters.R")
source("floa_rcb.R")
source("lenhoff_doris.R")
source("floa_point.R")
source("floa_roislien.R")
source("plot_loa.R")
source("get_coverage.R")
source("get_coverage_fraction.R")
source("get_coverage_singlecurve.R")
source("get_coverage_singlecurve_fraction.R")
source("crossval_coverage.R")
source("crossval_coverage_fraction.R")
source("singlecurve_coverage.R")
source("singlecurve_coverage_fraction.R")
source("plot_cov_ver.R")
# source("distance_2_floa.R")
source("estimate_uncertainty_loa.R")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_realistic", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_trend", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "non_gaussian", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "shift", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "imu_mc", dir.data)

floa.point <- floa_point(data)
floa.roislien <- floa_roislien(data)
floa.lenhoff <- floa_lenhoff(data, k_reihe = 50, n.boot = n.boot, cp.begin = 0, alpha = 0.05)

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

covered.curves.percent <- apply(cover.cross.singlecurve, 2, calculate_percent)
covered.curves.percent <- data.frame(t(covered.curves.percent))
colnames(covered.curves.percent) <- c("Point", "Roislien", "Lenhoff")

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
colnames(cover.cross.mean.sd) <- c("Point", "Roislien", "Lenhoff")

knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")

@@

<!-- c. Average distance to the outer point of the curve set -->
<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v2") -->
<!-- floa.point <- floa_point(data) -->
<!-- floa.roislien <- floa_roislien(data) -->

<!-- dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist, -->
<!--                        distance_2_floa(data, floa)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.point)$upr.dist, -->
<!--                        distance_2_floa(data, floa.point)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$upr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$lwr.dist -->
<!--                        ) -->

<!-- colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw") -->

<!-- boxplot(dist.all, ylab = "floa boundary - curve maximum") -->
<!-- ``` -->

c. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
# estimate_uncertainty_loa(data, n.boot)
```

@@

<!-- c. Average distance to the outer point of the curve set -->
<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v2") -->
<!-- floa.point <- floa_point(data) -->
<!-- floa.roislien <- floa_roislien(data) -->

<!-- dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist, -->
<!--                        distance_2_floa(data, floa)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.point)$upr.dist, -->
<!--                        distance_2_floa(data, floa.point)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$upr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$lwr.dist -->
<!--                        ) -->

<!-- colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw") -->

<!-- boxplot(dist.all, ylab = "floa boundary - curve maximum") -->
<!-- ``` -->

c. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
# estimate_uncertainty_loa(data, n.boot)
```

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
colnames(cover.cross.mean.sd) <- c("Point", "Roislien", "Lenhoff")

knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")
```

<!-- c. Average distance to the outer point of the curve set -->
<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v2") -->
<!-- floa.point <- floa_point(data) -->
<!-- floa.roislien <- floa_roislien(data) -->

<!-- dist.all <- data.frame(distance_2_floa(data, floa)$upr.dist, -->
<!--                        distance_2_floa(data, floa)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.point)$upr.dist, -->
<!--                        distance_2_floa(data, floa.point)$lwr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$upr.dist, -->
<!--                        distance_2_floa(data, floa.roislien)$lwr.dist -->
<!--                        ) -->

<!-- colnames(dist.all) <- c("floa.up", "floa.lw", "point.up", "point.lw", "roislien.up", "roislien.lw") -->

<!-- boxplot(dist.all, ylab = "floa boundary - curve maximum") -->
<!-- ``` -->

c. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
# estimate_uncertainty_loa(data, n.boot)
```

@@

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
colnames(cover.cross.mean.sd) <- c("Point", "Roislien", "Lenhoff")

knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")
